Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-07-15 R0V0.tex
> Done: Must of the introduction.
> Do: Review some parts of the introduction. Maybe emphasize about the distributed integration of the controller and review the conclusion.

\usepackage[natbib=true,backend=bibtex,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource{../../../Library.bib}
\AtBeginBibliography{\small}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org.}% <-this % stops a space
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

@@

For linear systems, the problem of design controllers with a prescribed structure is known to be NP-hard \cite{BlondelTsitsiklis1997}. Consequently, for nonlinear systems, it is \emph{at least} NP-hard.

\paragraph{Overview.} The motivation and background needed for this paper are stated in Section \ref{sec:Background and Motivation}. The problem under consideration is formalized in Section \ref{sec:Problem Formulation}. Section \ref{sec:Results} presents the result of this paper. Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}. The proofs of the results are provided in Section \ref{sec:Proof of the Results}. Section \ref{sec:Conclusion} collects final remarks.

@@

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology) for network systems rendering it universally stabilizable. Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example system:i}
	\dot{x}_i=??
\end{equation}
Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example system:i}.

\subsection{Background}

@@

A suitable framework to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by $A_{jk}(x,u)=\tfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)$
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem \cite{Rantzer:2001}. The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.

Step 1 (Offline LMI computation). Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$. The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following linear matrix inequality (LMI)
\begin{equation}\label{eq:LMI formulation}
	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\preceq0,
\end{equation}
for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.

@@

{\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$. Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the LMI \eqref{eq:contracting feedback law}.

@@

Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$. Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i},
	\end{equation*}
for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.

Although the requirement of a control-contraction metric $M$ to have block-diagonal structure may be restrictive, for positive linear time-invariant systems the existence of a matrices $P=P^\top\succ0$ with diagonal structure is not conservative \cite{Tanaka2011}. Thus, the question of how restrictive is the requirement of $M$ to be diagonal is open. The main result of the paper is stated below.

\todo[inline]{Compare SS-CCM with SS-LF from \cite{Dirr2015,Rantzer2013}}

To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the LMI \eqref{eq:LMI formulation}.

For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{equation*}
		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
	\end{equation*}
	and
	\begin{align*}
		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
		\text{has the property}&\ \mathscr{K}_Y(i)\}.
	\end{align*}
\end{subequations}
Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI \eqref{eq:LMI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the LMI \eqref{eq:LMI formulation} is cannot be done in parallel. The next result provides sufficient conditions to solve each component \eqref{eq:LMI formulation} independently, and according to the structure defined by the set $\Xi$. Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

@@

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI
	\begin{equation}\label{eq:LMI formulation:i}
		T_{ii}\preceq 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the LMI \eqref{eq:LMI formulation}.
\end{corollary}

@@

@@

Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
\begin{equation}\label{eq:example}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.
\end{equation}
where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

For each index $i\in\mathbb{N}_{[1,N]}$, define the vectors $q_i=(x_i,y_i)$, $\breve{q}_i=(x_{i-1},x_{i+1})$ and let $q=(q_1,\ldots,q_N)$. Denote also
\begin{align*}
	f_i(q_i,\breve{q}_i)=&\begin{bmatrix}
		-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		0
	\end{bmatrix}\\
	B_i=&\begin{bmatrix}
	0\\ 1
	\end{bmatrix}.
\end{align*}

@@

Employing the method provided in Theorem~\ref{thm:main result}, the LMI \eqref{eq:LMI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$.

@@

In the first one, no constraints were imposed on the matrix $Y$. The parser took 97 seconds to solve the  LMI \eqref{eq:LMI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:general}
		Y=\scalebox{0.75}{$\begin{bmatrix}
			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1+0.003x_3y_1,&0.005y_1y_3,&-0.007y_1+0.001x_4y_1,&0\\
			-0.008y_2-0.002x_1y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.007y_2-0.004x_3y_2,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.004x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.008y_3+0.002x_4y_3,&0\\
			-0.009y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
		\end{bmatrix}$}
\end{equation}
\end{figure*}

In the second case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The time taken by the parser to solve the LMI \eqref{eq:LMI formulation} was 98 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.32,1.59\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.61\right).
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{align*}
	Y_{ij}=&-3y_i-0.03x_iy_i&i,j\in\mathbb{N}_{[1,4]}\\
	Y_{12}=&-4-0.01x_1-y_1^2-y_2^2-2x_1^2-x_2^2\\	
	Y_{24}=&-3-0.01x_2-y_1^2-y_2^2-y_3^2-x_1^2-x_2^2-x_3^2\\	
	Y_{36}=&-3-0.01x_3-y_2^2-y_3^2-y_4^2-x_2^2-x_3^2-x_4^2\\	
	Y_{48}=&-4-0.01x_4-y_4^2-y_3^2-2x_4^2-x_3^2
\end{align*}

>>>>

\usepackage[natbib=true,backend=bibtex,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource{../../../../Library.bib}
\AtBeginBibliography{\small}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor ORCID}

@@

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org. ORCID: 0000-0002-0883-0231, }% <-this % stops a space
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem under consideration is to design structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design these feedback laws, in terms of dynamical programming, the search for these functions is non-convex \cite{Rantzer:2001}. On the other hand, control-contraction metrics provide controllers that render pairs of solutions exponentially converge to each other. Moreover, the search for a structured controller and a suitable metric can be formulated in terms of a convex optimization problem. Under block-diagonal dominance conditions, this convex optimization problem can also be distributed. An example illustrate the approach for a network system.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Nonlinear Systems, Feedback Design, Contraction Theory, Distributed Control, Network Systems
\end{IEEEkeywords}

@@

Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. The main concept employed for the control of dynamic systems is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of dynamic programming.

For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.

In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}. In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.

For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}. However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}). In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.

An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below). This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has several states (large scale), it does not scale well. This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).

Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}. For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems, i.e., to make the controller scalable. In some cases, this property is satisfied by desnigning controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).

In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems. Consequently, for nonlinear systems the problem is very challenging.

In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}. Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure. The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to reduce the number of LMIs to be solved.

For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}. The case can be even worse, when structural constraints are considered.

For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs, in this work. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed similarly to Lyapunov functions to measure the exponential convergence of pairs of solutions. Employing CCMs, the design of a structured feedback law allowing exponential convergence of solution is obtained in two steps.

The first step consists of an off-line computation. The original system is extended with its \emph{differential / variational} formulation. The exponential convergence is reformulated in terms of stability of the origin for the extended system. This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint. The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law.

The second step consists of an on-line integration. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).

\todo[inline]{Highlight the difference between this paper and \cite{Manchester2014a} by saying that this one the integration part is also distributed.}

At this point, the three contributions of this work can be highlighted. First, a systematic framework for off-line computation of a structured controller and metric for nonlinear systems is provided. This framework is the formulation of a convex optimization problem whose computation can also be distributed, provided that some conditions are met. Second, the computation of the online integration phase can distributed, due to the structure imposed on the metric. Third, the structure impose on the controller allows to address the scalability issue of CCMs. Note that the proposed method provides an explicit formula for the controller, since it is constructive.

Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature. These are mostly related to network systems. For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis. This paper contrast with these works mainly in two points: 1) A systematic framework  for structured controller design is proposed; 2) Due the formulation of the stabilization as a convex optimization problem, not only a explicit formula of a structured controller is obtained but also a metric.

\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}. The background needed for this paper is stated in Section \ref{sec:background}. Section \ref{sec:Results} presents the result of this paper. Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}. The proofs of the results are provided in Section \ref{sec:Proof of the Results}. Section \ref{sec:Conclusion} collects final remarks.

@@

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology) for network systems rendering it universally stabilizable. Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.
\end{equation}
Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example}.

\subsection{Background}\label{sec:background}

@@

A suitable framework to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by 
\begin{equation*}
	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
\end{equation*}
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.

Step 1 (Offline MI computation). Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$. The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
\begin{equation}\label{eq:MI formulation}
	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\preceq0,
\end{equation}
that is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.

@@

{\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$. Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:contracting feedback law}.

@@

Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$. Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i),
	\end{equation*}
for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.

In other words, a sum-separable metric is the case in which the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these components depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$. The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).

To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.

For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{equation*}
		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
	\end{equation*}
	and
	\begin{align*}
		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
	\end{align*}
\end{subequations}
Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel. The next result provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$. Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

@@

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
	\begin{equation}\label{eq:MI formulation:i}
		T_{ii}\preceq 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
\end{corollary}

@@

\subsection{Discussion}

Although the requirement of a sum-separable structure seems to be restrictive, for some classes of systems this structure is equivalent to the (possibly local) stability of the origin.

For monotone systems (i.e., systems for which the some order of initial conditions is preserved along the flow of the vector field) described by a vector field that is continuously differentiable and whose gradient matrix is Hurwitz at the origin, there exists a sum-separable Lyapunov function in a neighborhood of the origin \cite[Theorem 3.4]{Dirr2015}.

For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.

Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure is open. As mentioned before, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.

@@

A case where structured controller design is important is on distributed design for network systems.

Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
\begin{equation}\tag{\ref{eq:example}}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.
\end{equation}
where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

For each index $i\in\mathbb{N}_{[1,N]}$, define the vectors $q_i=(x_i,y_i)$, $\breve{q}_i=(x_{i-1},x_{i+1})$ and let $q=(q_1,\ldots,q_N)$. Denote also
\begin{align*}
	f_i(q_i,\breve{q}_i)=&\begin{bmatrix}
		-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		0
	\end{bmatrix}\\
	B_i=&\begin{bmatrix}
	0, 1
	\end{bmatrix}^\top.
\end{align*}

@@

Employing the method provided in Theorem~\ref{thm:main result}, the MI \eqref{eq:MI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$. The hardware on which the software ran is an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.

@@

In the first one, no constraints were imposed on the matrix $Y$. The parser took  seconds to solve the  MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:general}
		Y(q)=\scalebox{0.75}{$\begin{bmatrix}
			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1+0.003x_3y_1,&0.005y_1y_3,&-0.007y_1+0.001x_4y_1,&0\\
			-0.008y_2-0.002x_1y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.007y_2-0.004x_3y_2,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.004x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.008y_3+0.002x_4y_3,&0\\
			-0.009y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
		\end{bmatrix}$}
\end{equation}
\end{figure*}

In the second case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience $q_0=q_1$ and $q_5=q_4$).
